Tidal field anisotropy as a tracer of cosmic voids

### 2015-01-06 cosmic_voids.tex
updated presentation of the method, removed ellipticity-prolateneess

%*************************************************************************
\section{Algorithms to quantify the Cosmic Web}
\label{sec:algorithms_cosmic_web}
%*************************************************************************

@@

This scheme was initially proposed by \citet{Hahn07} as a novel 
alternative for classifying the Cosmic Web based on the tidal tensor, 
that is somehow more fundamental than the density field as it also allows 
to quantify the orbital dynamics of the matter field. This approach 
consists of a second-order expansion of the equations of motion around 
local minima of the gravitational potential and then extended to any 
position. The second-order term corresponds to the tidal tensor, which is
defined as the Hessian matrix of the normalized gravitational potential

%.........................................................................
%Tidal Tensor
\eq{V_web}
{	T_{\alpha\beta} = \frac{\partial^2\phi}{\partial x_{\alpha}\partial x_{\beta}}	}
%.........................................................................
where the physical gravitational potential has been rescaled by a factor 
$4\pi G\bar{\rho}$ in such a way that $\phi$ satisfies the following 
equation

@@

Since the tidal tensor can be represented in any cell by a real and 
symmetric $3\times 3$ matrix, it is ensured the possibility to diagonalize 
it and obtain three real eigenvalues $\lambda_{1}\geq\lambda_{2}\geq
\lambda_3$. This set of eigenvalues can be used as indicators of the local 
orbital stability in each proper direction, which in turn can be 
translated into a classification scheme of the Cosmic Web. A counting of 
the number of positive (stable) or negative (unstable) eigenvalues allows 
to catalogue a single cell into one of the next four types of environment: 
voids (3 negatives eigenvalues), sheets (2), filaments (1) and knots (0). 
A significant improvement to this scheme was introduced by \citet{Forero09}
by means of a relaxation of the stability criterion. The relative strength 
of each eigenvalue is no longer defined by the sign, but instead by a
threshold value $\lambda_{th}$ that can be tuned in such a way that the
visual impression of the web-like matter distribution is reproduced.

@@

We also use a kinematical scheme to define the Cosmic Web environment in 
the simulation. The scheme has been thoroughly described in 
\citet{Hoffman12} and applied to study the shape and spin alignment in the
Bolshoi simulation in \citet{Libeskind13}. We refer the reader to these 
papers to find a detailed description of the algorithm, its limitations 
and capabilities. The Vweb scheme for environment finding is based on the
local velocity shear tensor calculated from the smoothed dark matter 
velocity field in the simulation. The central quantity is given by the 
following dimensionless expression

%.........................................................................
%V-Web Definition
\eq{V_web}
{	\Sigma_{\alpha\beta} = -\frac{1}{2H_0}\pr{\frac{\partial v_{\alpha}}
{\partial x_{\beta}}+\frac{\partial v_{\beta}}{\partial x_{\alpha}}}	}
%.........................................................................
where $v_{\alpha}$ and $x_{\alpha}$ represent the $\alpha$ component of 
the comoving velocity and position, respectively. Like the tidal tensor, 
$\Sigma_{\alpha\beta}$ can be represented by a $3\times 3$ symmetric 
matrix with real values, hence diagonalizing it is obtained three real 
eigenvalues $\lambda_{1}\geq\lambda_{2}\geq\lambda_3$ whose sum (the 
trace of $\Sigma_{\alpha\beta}$) is proportional to the divergence of the 
local velocity field smoothed on the physical scale ${\mathcal R}$.

In the same way, the relative strength of the three eigenvalues with 
respect to a threshold value $\lambda_{th}$ allows for the local 
classification of the matter distribution into the previous four web types. 
For the threshold choosing in both schemes, the Tweb and the Vweb, it is
usual to fine-tuning the value in such a way that the visual appearance of
the Cosmic Web as seen in simulations and galaxy surveys is reproduced. 
However, we do not take this approach here, instead we propose a novel 
approach for the threshold choosing based on the maximization of the 
fractional anisotropy field occurring in filaments and very dense walls.

@@

The fractional anisotropy (FA), as developed by \citet{Basser95}, was 
conceived to quantify the anisotropy degree of a diffusion process, e.g. 
the diffusivity of water molecules through cerebral issue in nuclear
magnetic resonance imaging. Here we propose the FA, much in the same 
way as \citet{Libeskind13}, as a tracer of cosmic voids.

%.........................................................................
%Fractional anisotropy
\eq{fractional_anisotropy}
{ FA = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
(\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
\lambda_2^2 + \lambda_3^2} } }
%.........................................................................
where the eigenvalues are taken from either the Tweb or the Vweb 
(FA-Tweb and FA-Vweb respectively). Such as it is defined, $FA=0$ 
corresponds with an isotropic dynamic and $FA=1$ with a highly anisotropic 
distribution.

In left panels of Fig. \ref{fig:FA_field} we calculate the FA for both 
web schemes over a slide of the simulation. Some important points can be 
concluded from this figure:

%.........................................................................
\begin{itemize}
\item Voids display a highly isotropic expanding dynamic at their centres, 
becoming gradually more anisotropic at outer regions.
\item Knots feature with very isotropic collapses. For the Tweb, the FA 
exhibits very narrow distribution around knots. For the Vweb, these
distributions are more spread out, thereby indicating strong differences 
between the density and the velocity fields in highly non-linear regions.
\item The filamentary structure of the Cosmic Web is well traced by high 
FA values (black regions), thus indicating very anisotropic dynamics for 
sheets and filaments.
\item The FA, unlike the density field, displays a non-monotonic behaviour, 
where low values are characteristic of central regions of voids, reaching 
high values in sheets and filaments and becoming low again in knots. 
%\item The density field poorly traces the Cosmic Web. This is a somehow 
%expected result due to the semi-infinite range of the density field, what 
%makes more difficult to trace structures.
\end{itemize}
%.........................................................................

\subsection{Watershed algorithm}
\label{sec:watershed}

This algorithm is parameter-free and does  not require any assumption
on the shape and morphology of voids.  
Although we use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a 
Cartesian mesh for estimating the density and tensor fields, instead of 
the more sophisticated \textit{Delaunay tessellation for field estimator} 
(\texttt{DTFE}) technique \citep{Schaap00}, our implementation of the 
watershed transform should not be significantly affected as we are 
interested in low density regions where the \texttt{CIC} gives similar 
estimations.

%-------------------------------------------------------------------------
\subsection{Voids using web schemes}
\label{subsec:web_voids}
%-------------------------------------------------------------------------

For both web schemes, voids are regions where $\lambda_3\leq\lambda_2\leq
\lambda_1\leq\lambda_{th}$. This implies that the outlines of voids
are completely fixed by the relative strength of the $\lambda_1$ 
eigenvalue with respect to the threshold value. Therefore, as we 
increase/decrease the threshold value $\lambda_{th}$, voids expand/diminish
progressively through contours of $\lambda_1$. In Fig. 
\ref{fig:L1_correlations} we calculate the distribution of the FA as well
as of the density field with respect to $\lambda_1$ over all cells of the 
grid.

From Fig. \ref{fig:L1_correlations} we conclude that the FA is a good
tracer of voids as is almost perfectly correlated with low values of 
$\lambda_1$. Then, it reaches a maximum value, namely sheets and filaments, 
for finally reaching knots, which feature low FA values. This behaviour can 
be thought as a sort of one-dimensional tomography of the Cosmic Web. This
characteristic allows us to propose an optimal threshold value for both 
web schemes where the FA is maximized. Specifically we propose a value of 
$FA=0.95$, corresponding with a threshold $\lambda_{opt}^T = 0.265$ for
the Tweb and $\lambda_{opt}^V = 0.175$ for the Vweb.  For a threshold 
above these values, voids would span over very anisotropic regions, which 
must correspond to sheets and filaments. A threshold below would imply 
very low volume filling fractions of voids and dominant sheets. Finally, 
the density field do not correlate well with $\lambda_1$ (as calculated 
for both web schemes), and due to its monotonic increase, an estimate of 
an optimal threshold is not as clear as for the FA.

Once set the optimal thresholds for the web schemes, we proceed in Fig. 
\ref{fig:FAShapeness} to sample the FA and the prolateness for a random 
sample of cells previously classified into one of the four environments. 
The prolateness is introduced here for differentiating sheets and filaments
featuring high FA values. In order to illustrate the underlying local 
dynamics sampled by the cells, we also sketch different spheroidal 
geometries according to the relative strength of each eigenvalue, and 
then, we associate them to different ranges of the FA and the prolateness. 
From this, we conclude sheets display very anisotropic distributions, 
namely above $FA=0.95$. They are also biased towards oblate geometries, 
however there are some elongated sheets as well. Filaments are not as 
anisotropic as sheets, ranging from middle up to high FA values. They 
exhibit prolate geometries, but a considerable fraction of them are biased 
towards slightly more oblate values. Voids and knots are the only 
environments featuring with low FA values, thus indicating very isotropic 
expanding/collapsing dynamics at their centres. However, voids span over 
a very wide range of FA and geometries, whereas knots only span over low 
to middle FA values and display a biased oblate geometry.

%-------------------------------------------------------------------------
\subsection{Identifying void regions through web schemes}
\label{subsec:identification}
%-------------------------------------------------------------------------

%*************************************************************************
\section{Numerical Experiments}
\label{sec:experiments}
%*************************************************************************

We use here an unconstrained cosmological simulation (the Bolshoi 
simulation) to identify the possible large scale environment and the 
distribution of cosmic voids at $z=0$. The Bolshoi simulation follows the 
non-linear evolution of a dark matter density field on a cubic volume of 
size $250$\hMpc sampled with $2048^3$ particles. The cosmological 
parameters in the simulation are $\Omega_{\rm m}=0.27$, $\Omega_{\Lambda}
=0.73$, $h=0.70$, $n=0.95$ and $\sigma_{8}=0.82$ for the matter density, 
cosmological constant, dimensionless Hubble parameter, spectral index of 
primordial density perturbations and normalization for the power spectrum
respectively, consistent with the seventh year of data of the Wilkinson 
Microwave Anisotropy Probe (WMAP) \citep{Jarosik11}. For more detailed 
technical information about the simulation, see \citet{Klypin11}.

For estimating the density and velocity fields we use a 
\textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
cells, corresponding to a resolution of $0.98$\hMpc per cell side. Then, 
through finite-differences and FFT methods the tidal and shear tensors 
are computed. Finally, the eigenvalues and eigenvectors of the tensor are
obtained for each cell of the grid. Neglecting substructures presented 
below Megaparsec scales and taking into account our focus in voids, which
are a prominent characteristic of the Megaparsec Universe, we apply a 
Gaussian softening of one cell to all fields.

@@

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
\centering

  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
  \vspace{0.1 cm}
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}

  \captionof{figure}{\small Left panels show the visual impression of the 
  FA field over a slide of the simulation for each web scheme (T-web, upper 
  panels. V-web, middle panels). Black regions correspond with high values, 
  i.e. FA$\approx 1$, while white and light yellow regions to FA$\approx 0$. 
  It is worth noting the degeneration of low values of FA for knots and 
  central regions of voids, thus indicating a high isotropy for both 
  processes. In the same way, high values of FA are consistent with the 
  anisotropic geometry exhibited by filaments and very flat sheets. Middle 
  panels sketch the components of the Cosmic Web using the optimal threshold 
  values. Voids corresponds with white, sheets to gray, filaments to dark 
  gray and knots with black regions. Finally right panels sketch the 
  distribution of the catalogued voids by our method.}

  \label{fig:FA_field}

\end{figure*}
%.........................................................................

%.........................................................................
%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{flushleft}
\begin{figure*}
\centering

%.........................................................................
%FIGURE 3: FA of some regions and shape illustration
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/FA_Prolatenes_Vweb.pdf}
  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/FA_Prolatenes.png}

  \captionof{figure}{\small Fractional anisotropy and prolateness for a 
  random sample of cells (left panel) and for different spherical 
  geometries (right panel). For the cells, each environment is coded with
  a different colour, i.e. voids corresponds with dark blue points, 
  sheets with green, filaments with orange and knots with cyan. The axis 
  of the spheroids are computed from the relative strengths of the 
  eigenvalues, so their shape sketch the relative expanding/collapsing 
  dynamics into each direction.}

  \label{fig:FAShapeness}
  \vspace{0.1 cm}

>>>>

%*************************************************************************
\section{Algorithms to label the Cosmic Web}
\label{sec:algorithms_cosmic_web}
%*************************************************************************

@@

This scheme was initially proposed by \citet{Hahn07} as an
alternative for classifying the Cosmic Web based on the tidal tensor.
The tidal tensor allows a classification in terms of the orbital
dinamics of the matter field
This approach extends to second-order the equations of motion around 
local minima of the gravitational potential. 
The second-order term corresponds to the tidal tensor, which is
defined as the Hessian matrix of the normalized gravitational
potential.

%.........................................................................
%Tidal Tensor
\eq{V_web}
{	T_{\alpha\beta} = \frac{\partial^2\phi}{\partial x_{\alpha}\partial x_{\beta}},	}
%.........................................................................
where the physical gravitational potential has been rescaled by a
factor of   $4\pi G\bar{\rho}$ in such a way that $\phi$ satisfies the following 
Poisson equation

@@

Since the tidal tensor can be represented by a real and  symmetric
$3\times 3$ matrix, it is always possible to diagonalize  
it and obtain three real eigenvalues $\lambda_{1}\geq\lambda_{2}\geq
\lambda_3$ with its corresponding eigenvectors ${\bf u}_{1}$, ${\bf u}_{2}$,
${\bf u}_{3}$. 
This set of eigenvalues are indicators of the local  orbital stability
in each direction ${\bf u}_i$, which is to label the Cosmic Web.
The number of positive (stable) or negative (unstable) eigenvalues allows 
to label a location into one of the next four types of environment: 
voids (3 negatives eigenvalues), sheets (2), filaments (1) and knots (0). 
A modification to this scheme was introduced by \citet{Forero09}
by means of a relaxation of the stability criterion. The relative strength 
of each eigenvalue is no longer defined by the sign, but instead by a
threshold value $\lambda_{\rm th}$ that can be tuned in such a way
that the visual impression of the web-like matter distribution is
reproduced.

@@

We also use a kinematic scheme to define the Cosmic Web environment in 
the simulation, which has been thoroughly described in 
\cite{Hoffman12}.
This scheme has been used to study the shape, spin and peculiar
velocity alignments of dark matter halos with the cosmic web
\citep{Libeskind13,Forero2014}. 
We refer the reader to these papers to find a detailed description of
the algorithm, its limitations  and capabilities.    
The Vweb scheme for environment finding is based on the
local velocity shear tensor calculated from the smoothed dark matter 
velocity field in the simulation. This tensor is given by the 
following expression

%.........................................................................
%V-Web Definition
\eq{V_web}
{	\Sigma_{\alpha\beta} = -\frac{1}{2H_0}\pr{\frac{\partial v_{\alpha}}
{\partial x_{\beta}}+\frac{\partial v_{\beta}}{\partial x_{\alpha}}},}
%.........................................................................
where $v_{\alpha}$ and $x_{\alpha}$ represent the $\alpha$ component of 
the comoving velocity and position, respectively. Like the tidal tensor, 
$\Sigma_{\alpha\beta}$ can be represented by a $3\times 3$ symmetric 
matrix with real values, making it possible to find three real
eigenvalues and its corresponding eigenvectors.
%$\lambda_{1}\geq\lambda_{2}\geq\lambda_3$.
%whose sum (the 
%trace of $\Sigma_{\alpha\beta}$) is proportional to the divergence of the 
%local velocity field smoothed on the physical scale ${\mathcal R}$.

In this case we also use the relative strength of the three eigenvalues with 
respect to a threshold value $\lambda_{th}$ to classify the cosmic web
in the four web types we have already described.

Usually, the threshold is a free parameter that is tuned to reproduce
the visual appearence of the comic web. 
In this paper we take a different approach.
We find the optimal value of the threshold based on the maximization
of the fractional anisotropy field in the locations label as filaments
and walls.

\section{Numerical Simulations}
\label{sec:simulatins}

We use the Bolshoi simulation to test the method describe in the
paper. 
This simulation follows the non-linear evolution of a dark
matter density field on a cubic volume of  size $250$\hMpc sampled
with $2048^3$ particles. 
The cosmological parameters in the simulation are $\Omega_{\rm m}=0.27$,  $\Omega_{\Lambda}  =0.73$, $h=0.70$,
$n=0.95$ and $\sigma_{8}=0.82$ for the matter density,   cosmological
constant, dimensionless Hubble parameter, spectral index of
primordial density perturbations and normalization for the power
spectrum, respectively. 
This values are consistent with the seventh year of data of the Wilkinson 
Microwave Anisotropy Probe (WMAP) \citep{Jarosik11}. 
For more detailed  technical information about the simulation, see
\citet{Klypin11}.

We find the cosmic web we estimate first the density and velocity
fields using a  \textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
cells, corresponding to a spatial resolution of $0.98$\hMpc per cell
side.  
These fields are smoothed with a gaussian filter with a width of
$\sigma=0.98$\hMpc. 
We compute the tidal and shear tensors through finite-differences and
Finally, the eigenvalues and eigenvectors of the tensor are
obtained for each grid cell.
The data we use here is publicly available through the MultiDark
database \url{http://www.multidark.org/MultiDark/} which is described
in \citet{Riebe11}.

@@

The fractional anisotropy (FA), as developed by \citet{Basser95}, was 
conceived to quantify the anisotropy degree of a diffusion process, e.g. 
the diffusivity of water molecules through cerebral tissue in nuclear
magnetic resonance imaging. 
Here we propose the FA, much in the same way as \citet{Libeskind13},
as a tracer of cosmic voids.

The FA is defined as follows.
%.........................................................................
%Fractional anisotropy
\eq{fractional_anisotropy}
{{\mathrm{FA}} = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
(\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
\lambda_2^2 + \lambda_3^2} },}
%.........................................................................
where the eigenvalues are taken from either the Tweb or the Vweb 
(FA-Tweb and FA-Vweb respectively). Such as it is defined, FA$=0$ 
corresponds to an isotropic distribution ($\lambda_1=\lambda_2=\lambda_3$) and FA$=1$ with a highly anisotropic 
distribution.

In left panels of Fig. \ref{fig:FA_field} we show the FA field for both 
web schemes over a slide of the simulation. 
From this Figure we can observe that both voids and knots display a highly isotropic
expanding dynamic at their centres, becoming gradually more
anisotropic at outer regions. 
On the other hand the filamentary structure is traced by high FA
values. These characteristics are the key to use the FA as a tracer of
cosmic voids.

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
  \vspace{0.1 cm}
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
  \caption{Left colum. Visual impression of the 
  FA field over a slide of the simulation for each web scheme (T-web, upper 
  panels. V-web, middle panels). 
  Middle column. Components of the Cosmic Web using $\lambda_{th}$
  values that put an upper bound of $FA=0.95$ to voids. Voids
  corresponds with white, sheets to gray, filaments to dark gray and
  knots with black regions. 
  Right column. Sketches the distribution of the catalogued voids by
  our method.}
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

%-------------------------------------------------------------------------
\subsection{Fractional anisotropy as a void tracer}
\label{subsec:web_voids}
%-------------------------------------------------------------------------

%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{flushleft}
\begin{figure*}
\centering

Voids are regions where $\lambda_3\leq\lambda_2\leq
\lambda_1\leq\lambda_{th}$. 
This implies that a void is completely fixed by the relative strength
of the $\lambda_1$ eigenvalue with respect to the $\lambda_{th}$.   
As we  increase/decrease the threshold value $\lambda_{th}$, voids
increase/decrease progressively through contours of
increasing/decreasing $\lambda_1$.

Voids are thus characterized by low values of both FA and
$\lambda_1$. 
In Fig. \ref{fig:L1_correlations} we show that the these two values
are indeed closely correlated.  
The left panel shows the correlation between $\lambda_1$ and $FA$ for
all the grid cells in the simulation while the right panel shows the
correlation between $\lambda_1$ and the local overdensity $\delta$.  
This shows that the overdensity has a large scatter at fixed
$\lambda_1$.

From Figs. \ref{fig:FA_field} and \ref{fig:L1_correlations} we
conclude that the FA is a good tracer of voids as it is almost perfectly
correlated with low values of $\lambda_1$. 
We propose that voids should be composed completely by regions of
FA$<0.95$.
If we increase the values of $\lambda_1$ from its minimum until it
we reach FA$=0.95$ in \ref{fig1:L1_correlations} we find that this
correspond to critical values of $\lambda_{1}^T = 0.265$ and
$\lambda_{1}^V = 0.175$ for the Tweb and Vweb, respectively.
This means that setting $\lambda_{th}$ to either
$\lambda_{1}^T$/$\lambda_{1}^{V}$ automatically produces voids with
all the cells $FA<0.95$.   
The middle column in Fig. \ref{fig:FA_field} shows the web
classification for this choice of $\lambda_{th}$, demonstrating that
it is a sensible choice to define voids.

\subsection{Defining voids with a watershed algorithm}
\label{sec:watershed}

{\bf Reescribir para describir lo que hace el algoritmo}
This algorithm is parameter-free and does  not require any assumption
on the shape and morphology of voids.  
Although we use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a 
Cartesian mesh for estimating the density and tensor fields, instead of 
the more sophisticated \textit{Delaunay tessellation for field estimator} 
(\texttt{DTFE}) technique \citep{Schaap00}, our implementation of the 
watershed transform should not be significantly affected as we are 
interested in low density regions where the \texttt{CIC} gives similar 
estimations.

%Once set the optimal thresholds for the web schemes, we proceed in Fig. 
%\ref{fig:FAShapeness} to sample the FA and the prolateness for a random 
%sample of cells previously classified into one of the four
%environments.

%The prolateness is introduced here for differentiating sheets and filaments
%featuring high FA values. 
%In order to illustrate the underlying local 
%dynamics sampled by the cells, we also sketch different spheroidal 
%geometries according to the relative strength of each eigenvalue, and 
%then, we associate them to different ranges of the FA and the prolateness.

%From this, we conclude sheets display very anisotropic distributions, 
%namely above $FA=0.95$. They are also biased towards oblate geometries, 
%however there are some elongated sheets as well. Filaments are not as 
%anisotropic as sheets, ranging from middle up to high FA values. They 
%exhibit prolate geometries, but a considerable fraction of them are biased 
%towards slightly more oblate values. Voids and knots are the only 
%environments featuring with low FA values, thus indicating very isotropic 
%expanding/collapsing dynamics at their centres. However, voids span over 
%a very wide range of FA and geometries, whereas knots only span over low 
%to middle FA values and display a biased oblate geometry.

@@

%.........................................................................

%.........................................................................
%FIGURE 3: FA of some regions and shape illustration
%\begin{flushleft}
%\begin{figure*}
%\centering
%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
%  width=0.3\textheight]{./figures/FA_Prolatenes_Vweb.pdf}
%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
%  width=0.3\textheight]{./figures/FA_Prolatenes.png}

%  \captionof{figure}{\small Fractional anisotropy and prolateness for a 
%  random sample of cells (left panel) and for different spherical 
%  geometries (right panel). For the cells, each environment is coded with
%  a different colour, i.e. voids corresponds with dark blue points, 
%  sheets with green, filaments with orange and knots with cyan. The axis 
%  of the spheroids are computed from the relative strengths of the 
%  eigenvalues, so their shape sketch the relative expanding/collapsing 
%  dynamics into each direction.}

%  \label{fig:FAShapeness}
%  \vspace{0.1 cm}

%\end{figure*}
%\end{flushleft}
%.........................................................................
